### 2020-12-15 README.Rmd
updated readme and package vignette

The fasano.franceschini.test package is an R implementation of the 2-D Kolmogorov-Smirnov (KS) two-sample test as defined by Fasano and Franceschini (1987). This is a variant of the 2-D two-sample KS test as originally defined by Peacock (1983).

@@

#create 2-D samples with the different underlying distributions
sample1Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 3),
                          y = rnorm(n = 100,mean = 0, sd = 1))
sample2Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 1),
                          y = rnorm(n = 100,mean = 0, sd = 3))

@@

#create 2-D samples with the same underlying distributions
sample1Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 1),
                          y = rnorm(n = 100,mean = 0, sd = 1))
sample2Data <- data.frame(x = rnorm(n = 100,mean = 0, sd = 1),
                          y = rnorm(n = 100,mean = 0, sd = 1))

>>>>

The fasano.franceschini.test package is an R implementation of the 2-D Kolmogorov-Smirnov (**KS**) two-sample test as defined by Fasano and Franceschini (1987). This is a variant of the 2-D two-sample KS test as originally defined by Peacock (1983).

@@

#create 2-D samples with the different underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 3),
  y = rnorm(n = 100, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 1),
  y = rnorm(n = 100, mean = 0, sd = 3)
)

@@

#create 2-D samples with the same underlying distributions
sample1Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 1),
  y = rnorm(n = 100, mean = 0, sd = 1)
)
sample2Data <- data.frame(
  x = rnorm(n = 100, mean = 0, sd = 1),
  y = rnorm(n = 100, mean = 0, sd = 1)
)
